Reality or wishful thinking: Examining the feasibility of 15-minute neighborhoods from the perspective of network attributes

### 2023-07-06 Fifteen-minute-neighborhoods/Fifteen-minute-neighborhoods-title-page.Rmd
Repaired renv.lock

bibliography: bibliography.bib
biblio-style: spphys
# bibstyle options spbasic(default), spphys, spmpsci
output: rticles::springer_article
---

>>>>

bibliography: 
  - "`r system('kpsewhich ../bibliography/bibliography.bib', intern=TRUE)`"
biblio-style: spphys
# bibstyle options spbasic(default), spphys, spmpsci
output: rticles::springer_article
---
